More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
minor changes

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
\begin{mathpar} 
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak transition can be written as a series of tau transitions, hence by simplification we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

>>>>

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$
